---
title: "Here's my data"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

.
<br><br>
*You're welcome to use the data and code (with proper credit)*.

---

Alon-Barkat, Saar, and Sharon Gilad. 2017. "Compensating for Poor Performance with Promotional Symbols: Evidence from a Survey Experiment". *Journal of Public Administration Research and Theory*. 27(4): 661-675. DOI: [10.1093/jopart/mux013](https://doi.org/10.1093/jopart/mux013).  
<br>
Data is based on online survey experiment conducted on December 2015.
Replication materials available online at ['github.com/saaralonbarkat/IEC_2015'](https://github.com/saaralonbarkat/IEC_2015). 
<br>
```{r , include=FALSE, echo=FALSE}
PROMSYMB = read.csv("C:/SAAR/UNIVERSITY/R/site/DATA_files/PROMSYMB.csv")
```

<br>

```{r , warning = FALSE, message = FALSE,echo=FALSE}
require(rpivotTable)
require(dplyr)
PROMSYMB_01 = PROMSYMB %>%
  select(SYMBOL,AREA,EVALUATION_index,SATISFACTION,TRUST)
rpivotTable(PROMSYMB_01)
```
<br>


---

<br>

Gilad, Sharon, **Saar Alon-Barkat**, and Alexandr Braverman. 2016. "Large-Scale Social Protest: A Business Risk and a Bureaucratic Opportunity". *Governance* 29(3): 371-392. DOI: [10.1111/gove.12173](https://doi.org/10.1111/gove.12173).  

**Alon-Barkat, Saar**, and Sharon Gilad. 2016. "Political control or legitimacy deficit? Bureaucracies' symbolic responses to bottom-up public pressures". *Policy & Politics* 44(1): 41-58. DOI: [10.1332/030557315x14443003393944](https://doi.org/10.1332/030557315x14443003393944)

<br>
This project is based on a cross-sectional-time-series dataset that includes the advertising expenditures of 136 Israeli organizations (businesses, public organizations and NGOs) between 2010-2012 (half year periods), together with organizations' charecteristics. Data collected between 2013-2014.  
Replication materials available online at ['github.com/saaralonbarkat/PROTEST_2014'](https://github.com/saaralonbarkat/PROTEST_2014). 








