---
title: "Here's my data"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

.
<br><br>
> You're welcome to use the data. Make sure you're giving me credit and cite my work.

---

Alon-Barkat, Saar, and Sharon Gilad. 2017. "Compensating for Poor Performance with Promotional Symbols: Evidence from a Survey Experiment". *Journal of Public Administration Research and Theory*. 27(4): 661-675. DOI: [10.1093/jopart/mux013](https://doi.org/10.1093/jopart/mux013).  
<br>
```{r , include=FALSE, echo=FALSE}
PROMSYMB = read.csv("C:/Users/mr.saar/personal-site/DATA_files/PROMSYMB.csv")
```
Data from experiment (conducted on December 2015).
<br>

* [Questionnaire (Qualtrics)](https://github.com/saaralonbarkat/personal-site/raw/master/SAAR%20ALON%20BARKAT%20CV%207.9.17.pdf).

* [Dataset (csv format)](https://github.com/saaralonbarkat/personal-site/raw/master/SAAR%20ALON%20BARKAT%20CV%207.9.17.pdf).

* [R script](https://github.com/saaralonbarkat/personal-site/raw/master/SAAR%20ALON%20BARKAT%20CV%207.9.17.pdf).  

<br>


```{r , warning = FALSE, message = FALSE,echo=FALSE}
require(rpivotTable)
rpivotTable(PROMSYMB[,c("SYMBOL","AREA","EVALUATION_index","SATISFACTION","TRUST")], rendererName="Table")
```
<br>


---

<br>







